\bf\mftitle

### 2011-03-02 doc/jInfer/treeruledisplayer/treeruledisplayer.tex
last minute corrections + PDF

The main class implementing \code{RuleDisplayer} inference interface and simultaneously registered as its service provider is \code{TreeRuleDisplayer}. Main method of this class is \code{createDisplayer()}, which looks up the component, adds a new panel to it and renders the specified grammar in it.\\

@@

The diagram of classes involved in rule display is in figure \ref{figure-class-diagram}. Main window of rule displayer may have multiple tabs in it: each contains its own \code{RuleDisplayer} responsible for rendering specified grammar using \jmodule{JUNG} library. Each tab in rule displayer window is represented by instance of \code{RulePanel} which contains button linking to options and the main panel (canvas) with rendered rules. Canvas is created by \code{VisualizationViewer} instance with \code{TreeLayout} layout (which are both classes from JUNG library). For \code{VisualizationViewer}, \code{GraphMouse} is set with transforming mode to allows zooming and moving of graph in canvas. To allow the user to set custom appearance of rules, we set various \code{Transformer}s in \code{RenderContext} of \code{VisualizationViewer}. These transormers change color, shape and vertex size in each rule tree according to properties set in options.\\

All the trees representing rules are created in the \code{GraphBuilder} class using the \code{buildGraphPanel()} method. This method creates \code{DelegateForrest} of \code{DelegateTree}s where each tree of the forrest represents one rule. Each vertex of the tree is represented by \code{Regexp<?\ extends AbstractNamedNode>} and edge by \code{RegexpInterval}. While the code building tree structure is a nice recursion programming exercise, there is nothing of a special interest in it. Finally the method appends forrest into layout and \code{VisualizationViewer} which were described above. All code responsible for building rule trees is contained in the \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.logic}. For more details about JUNG library please see \cite{jung}.\\

@@

All settings provided by \jmodule{TreeRuleDisplayer} are NetBeans-wide. The options panel along with all the logic is in the \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.options} package. Available options include setting the color of the background, horizontal and vertical distance between vertices. Also for each type of vertex is possible to set the size, the shape and the color.

>>>>

The main class implementing \code{RuleDisplayer} inference interface and simultaneously being registered as its service provider is \code{TreeRuleDisplayer}. Main method of this class is \code{createDisplayer()}, which looks up the component, adds a new panel to it, and renders the specified grammar in it.\\

@@

The diagram of classes involved in the process of rule displaying is in figure \ref{figure-class-diagram}. Main window of rule displayer may have multiple tabs in it: each contains its own \code{RuleDisplayer} responsible for rendering specified grammar using \jmodule{JUNG} library. Each tab in rule displayer window is represented by instance of \code{RulePanel} which contains button linking to options and the main panel (canvas) with rendered rules. Canvas is created by \code{VisualizationViewer} instance with \code{TreeLayout} layout (which are both classes from JUNG library). For \code{VisualizationViewer}, \code{GraphMouse} is set with transforming mode to allows zooming and moving of graph in canvas. To allow the user to set custom appearance of rules, we set various \code{Transformer}s in \code{RenderContext} of \code{VisualizationViewer}. These transormers change color, shape and vertex size in each rule tree according to properties set in options.\\

All the trees representing rules are created in the \code{GraphBuilder} class using the \code{buildGraphPanel()} method. This method creates \code{DelegateForrest} of \code{DelegateTree}s where each tree of the forest represents one rule. Each vertex of the tree is represented by \code{Regexp<?\ extends AbstractNamedNode>} and edge by \code{RegexpInterval}. While the code building tree structure is a nice recursion programming exercise, there is nothing of a special interest in it. Finally, the method appends forrest into layout and \code{VisualizationViewer} which were described above. All the code responsible for building rule trees is contained in the \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.logic}. For more details about JUNG library please see \cite{jung}.\\

@@

All settings provided by \jmodule{TreeRuleDisplayer} are NetBeans-wide. The options panel along with all the logic is in \code{cz.cuni.mff.ksi.jinfer.treeruledisplayer.options} package. Available options include setting the color of the background, horizontal and vertical distance between vertices. Also, for each type of vertex, it is possible to set a size, shape and a color.
